Learning constraints in tabular data

### 2016-05-23 Paper/ECAI/tabular.tex
Introduce optimizations

\begin{example}
  \samuel{Is this still necessary?}
  Consider the template $\ecsumprod{x}{y}{z}$, then the generated CSP will contain three variables $V_x, V_y, V_z$ corresponding to arguments $x, y$ and $z$ respectively.
  Given blocks~\blocks, the domain of these variables are $D(V_x) = D(V_y) = D(V_z) = \{ 1, \dots, |\blocks| \}$.
  Finally, the signature will be translated into constraints:
  \begin{align*}
    & \numeric(V_x) \land \numeric(V_y) \land \numeric(V_z) \\
    & \por(V_x) = \mathit{row} \implies \pcols(V_x) = 1 \\
    & \por(V_x) = \mathit{row} \implies \prows(V_x) = 1 & \\
    & \plength(V_y) \geq 2 \land \plength(V_z) \geq 2 \\
    & \plength(V_y) = \plength(V_z)
  \end{align*}
  Every solution is a tuple of values for~$V_x$, $V_y$ and~$V_z$ corresponding directly with a superblock assignment over~\blocks.
\end{example}

@@

\samuel{MARKER-C}
\subsection{Implementation}

@@

\paragraph{Constraint solvers}
Generic constraint solving technology can be used for the candidate group generation as well as for enumerating the satisfying subgroups. Constraint solvers can be categorized as being stand-alone solvers, meaning that they have a text-based modeling language in which the CSP must be formulated, and \textit{embedded}, meaning that they have a programmatic API to formulate the CSP.

@@

\paragraph{Redundancy}
There are only types of redundancy that we eliminate during search. The first is the removal of symmetric attribute assignments as explained in Section~\ref{sec:algo:subgr}.

@@

\paragraph{Constraints}
The constraints that are currently supported in our system are shown in Table~\ref{table:constraints}. All these constraints are available in popular spreadsheet software, except the first two constraints (alldifferent and permutation). These two constraints are \textit{structural} constraints, which we added so they can be used in the signature of other constraint templates; they are also popular constraints in constraint satisfaction~\cite{modelseeker}.

>>>>

\begin{example}
  \samuel{Is this still necessary?}
  Consider the template $\ecsumprod{x}{y}{z}$, then the generated CSP will contain three variables $V_x, V_y, V_z$ corresponding to arguments $x, y$ and $z$ respectively.
  Given blocks~\blocks, the domain of these variables are $D(V_x) = D(V_y) = D(V_z) = \{ 1, \dots, |\blocks| \}$.
  Finally, the signature will be translated into constraints:
  \begin{align*}
    & \numeric(V_x) \land \numeric(V_y) \land \numeric(V_z) \\
    & (\por(V_x) = \mathit{row}) \implies (\pcols(V_x) = 1) \\
    & (\por(V_x) = \mathit{column}) \implies (\prows(V_x) = 1) & \\
    & \plength(V_y) \geq 2 \land \plength(V_z) \geq 2 \\
    & \plength(V_y) = \plength(V_z)
  \end{align*}
  Every solution is a tuple of values for~$V_x$, $V_y$ and~$V_z$ corresponding directly with a superblock assignment over~\blocks.
\end{example}

@@

\samuel{MARKER-C}
\subsection{Optimizations}
This section discusses various essential design decisions and optimizations.
The aim is to improve the algorithm in three areas: 1) speed; 2) redundant constraints; and 3) extensibility.

@@

\subsubsection{Constraint solvers}
Generic constraint solving technology can be used for the candidate group generation as well as for enumerating the satisfying subgroups. Constraint solvers can be categorized as being stand-alone solvers, meaning that they have a text-based modeling language in which the CSP must be formulated, and \textit{embedded}, meaning that they have a programmatic API to formulate the CSP.

@@

\subsubsection{Redundancy}
There are only types of redundancy that we eliminate during search. The first is the removal of symmetric attribute assignments as explained in Section~\ref{sec:algo:subgr}.

@@

\subsubsection{Constraints}
The constraints that are currently supported in our system are shown in Table~\ref{table:constraints}. All these constraints are available in popular spreadsheet software, except the first two constraints (alldifferent and permutation). These two constraints are \textit{structural} constraints, which we added so they can be used in the signature of other constraint templates; they are also popular constraints in constraint satisfaction~\cite{modelseeker}.
